Clustering time series based on probability distributions across temporal granularities

### 2021-11-17 main.Rmd
fig 7 caption

```{r opt-cluster-tsne-jsd, fig.cap = "(a) shows t-SNE summary of the $24$ selected customers chosen through prototype selection, (b) and (c) shows a plot of sindex for different cluster size for clustering based on JS-based distances and wpd-distances respectively. The plot suggests optimal number of clusters as $4$ and $7$ respectively."}
#include_graphics("figs/opt_clust_parenthesis.png")
```

>>>>

```{r opt-cluster-tsne-jsd, fig.cap = "Clustering summaries: t-SNE computed on the $24$ selected customers (a), and separation index ($sindex$) for 2-10 clusters using JS (b) and WPD (c). Various choices in number of clusters would be recommended. Four clusters are visible in t-SNE, although it might hide a fifth cluster because dimension reduction to 2D may be insufficient to see the difference. JS suggests 3 and wpd suggests 3 or 6."}
#include_graphics("figs/opt_clust_parenthesis.png")
```
